---
title: "SOC sequestration potential"
author: "Jacob Spertus"
date: "3/08/2023"
header-includes:
  -\usepackage{amsmath}
  -\usepackage{amsfonts}
output:
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(maps)
library(splines)
library(xtable)
library(hettx)
library(latex2exp)
library(Rforestry)
library(tictoc)
library(kableExtra)
library(ggnewscale)
library(grid)


source("R/functions.R")
```

# Plot potential trajectories
```{r}
time <- seq(0, 10, length.out = 100)
response_1 <- log(1 + 2*time)
response_2 <- 2 * (pnorm(0.5 * time) - 0.5)
response_3 <- -0.1 * time
response_4 <- time - (0.3 * (time))^2

pt_data <- data.frame(
  "x" = rep(time, 4), 
  "y" = c(response_1, response_2, response_3, response_4), 
  "scenario" = rep(c("Concave growth", "New equilibrium", "Locally linear loss", "Reversal"), each = length(time)))

pt_plot <- ggplot(pt_data, aes(x = x, y = y, color = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line(size = 1.5) + 
  theme_bw() +
  ylim(-1,10) +
  scale_colour_manual(values = c("steelblue", "firebrick", "forestgreen", "darkorange3")) +
  theme(
    text = element_text(size = 14), 
    axis.text.y = element_blank(), 
    axis.ticks.y = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.text = element_text(size = 14),
    legend.title = element_blank(),
    panel.border = element_blank(),
    legend.key.width = unit(1, "cm")) +
  labs(title = "Potential trajectories", x = "Time", y = "SOC change")

pt_plot
```

# Observed trajectory
```{r}
time <- seq(0, 10, length.out = 100)
response_1 <- log(1 + 2*time)
response_2 <- 2 * (pnorm(0.5 * time) - 0.5)
response_3 <- -0.1 * time
response_4 <- time - (0.3 * (time))^2

ot_data <- data.frame(
  "x" = rep(time, 4), 
  "y" = c(response_1, response_2, response_3, response_4), 
  "scenario" = rep(c("Concave growth", "New equilibrium", "Locally linear loss", "Reversal"), each = length(time)),
  "trajectory" = factor(rep(c("Realized", "Counterfactual", "Counterfactual", "Counterfactual"), each = length(time)), levels = c("Realized", "Counterfactual"))) 

ot_plot <- ggplot(ot_data, aes(x = x, y = y, color = scenario, linetype = trajectory)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line(linewidth = 1.5) + 
  theme_bw() +
  ylim(-1,10) +
  scale_colour_manual(values = c("steelblue", "firebrick", "forestgreen", "darkorange3")) +
  theme(
    text = element_text(size = 18), 
    axis.text.y = element_blank(), 
    axis.ticks.y = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.text = element_text(size = 14),
    legend.title = element_blank(),
    panel.border = element_blank(),
    legend.key.width = unit(1, "cm")) +
  labs(title = "Trajectories", x = "Time", y = "SOC change")

ot_plot
```

# Saturation as decreasing CATE and as Dose-Response

```{r}
#dose response
dose <- seq(0, 10, length.out = 100)
response_complete_saturation <- 6 * pnorm(dose/2) - 3
response_partial_saturation <- log(1 + 10*dose)
response_no_saturation <- dose
response_convex <- (dose/2)^2 /4
dr_data <- data.frame(
  "hypothesis" = "Dose-response",
  "x" = rep(dose, 4), 
  "y" = c(response_complete_saturation, response_partial_saturation, response_no_saturation, response_convex), 
  "scenario" = rep(c("Saturation", "Diminishing returns", "Linear storage", "Increasing returns"), each = length(dose)))

#conditional average treatment effect
baseline <- seq(0,5, length.out = 100)
CATE_moderation <- exp(-baseline)
CATE_nomoderation <- rep(0.5, length(baseline))
cate_data <- data.frame(
  "hypothesis" = "Saturation-moderation",
  "x" = rep(baseline, 2),
  "y" = c(CATE_moderation, CATE_nomoderation),
  "scenario" = rep(c("Complete saturation", "No Saturation"), each = length(baseline)))

combined_data <- bind_rows(dr_data, cate_data)

#dose response plot
dr_plot <- ggplot(dr_data, aes(x = x, y = y, color = scenario)) +
  geom_line(size = 1.5) + 
  geom_hline(yintercept = 3, linetype = 'dashed') +
  theme_bw() +
  scale_colour_manual(values = c("darkorange3", "steelblue", "forestgreen", "firebrick")) +
  theme(
    text = element_text(size = 18), 
    axis.text = element_blank(), 
    axis.ticks = element_blank(),
    legend.text = element_text(size = 14),
    legend.title = element_blank(),
    panel.border = element_blank(),
    legend.key.width = unit(1, "cm")) +
  labs(x = "Carbon inputs", y = "SOC change at equilibrium")

#CATE plot
cate_plot <- ggplot(cate_data, aes(x = x, y = y, color = scenario)) +
  geom_line(size = 1.5) + 
  theme_bw() +
  scale_colour_manual(values = c("steelblue","darkorange3")) +
  theme(
    text = element_text(size = 18), 
    axis.text = element_blank(), 
    axis.ticks = element_blank(),
    legend.text = element_text(size = 14),
    legend.title = element_blank(),
    panel.border = element_blank(),
    legend.key.width = unit(1, "cm")) +
  labs(title = "(a) Moderation", x = "Baseline SOC", y = "SOC sequestered")
```

```{r}
dr_plot
```

```{r}
cate_plot
```



# NRCS Study

The following data were collected by the Silver Lab from 7 paired treatment-control sites around California. Baseline topsoil samples were gathered and treatment was applied in 2016. The last top soil samples were gathered in 2019.

```{r read nrcs data}
# these data come from the file 'NRCS 7site 2016-2019.xlsx' sent by email from Whendee Silver on 9/22/2023: 
# I made two manual edits: 
  #(i) removed spaces in site names in order to parse with separate_wider_delim 
  #(ii) standardized "Tomkat"/"TomKat" to "TomKat" 
# I then renamed it 'silver_lab_nrcs_data.csv' and exported the xlsx to a csv
# note that in this analysis we treat cores (not plots) as independent replicates, which is technically pseudo-replication

nrcs_data <- read_csv("Data/silver_lab_nrcs_data.csv") %>%
  rename(samples = "Samples (same as 2018 & 2019)", TN = "%N", TC = "%C") %>%
  mutate(samples = gsub("cm ", "", samples)) %>%
  separate_wider_delim(samples, delim = " ", names = c("sample", "site", "depth_cm", "year")) %>%
  separate_wider_position(sample, c(treatment = 1, sample = 1)) %>%
  filter(depth_cm == "0-10") %>%
  filter(site != "BethelIsland") %>% 
  filter(year %in% c(2016, 2019)) %>%
  pivot_wider(names_from = "year", names_prefix = "TC_", values_from = "TC", id_cols = c("treatment", "sample", "site")) %>%
  mutate(treatment_long = ifelse(treatment == "T", "Compost", "Control")) %>%
  mutate(treatment = ifelse(treatment == "T", 1, 0)) 
glimpse(nrcs_data)
```


```{r estimate average treatment effect in NRCS}
# average treatment effect estimates (core-level)
ATE_dim <- mean(nrcs_data$TC_2019[nrcs_data$treatment == 1]) - mean(nrcs_data$TC_2019[nrcs_data$treatment == 0])
SE_dim <- sqrt(var(nrcs_data$TC_2019[nrcs_data$treatment == 1])/sum(nrcs_data$treatment == 1) + var(nrcs_data$TC_2019[nrcs_data$treatment == 0])/sum(nrcs_data$treatment == 0))
c(ATE_dim, SE_dim)
```

### Core-level results


```{r estimate effect of optimal policy if cate estimates are taken as groundtruth}
baseline_soc_grid <- seq(from = min(nrcs_data$TC_2016), to = max(nrcs_data$TC_2016), length.out = 100)
baseline_mean <- mean(nrcs_data$TC_2016)

# estimates for the study points
cates_nrcs_study <- estimate_cate(
  Y=nrcs_data$TC_2019, 
  Z=nrcs_data$treatment, 
  X=as.matrix(nrcs_data$TC_2016),
  learner = learner_ols
)

#outcome on blanket policy
blanket_optimum <- abs(ATE_dim)
rel_blanket_optimum <- 100 * blanket_optimum / baseline_mean

# outcome on unconstrained optimal policy
unconstrained_optimum <- mean(abs(cates_nrcs_study$cate))
rel_unconstrained_optimum <- 100 * unconstrained_optimum / baseline_mean
# treatment fraction for optimal policy
trt_frac <- mean(cates_nrcs_study$cate > 0)

# outcome on treat 10% optimal policy 
n_top_10_percent <- ceiling(length(cates_nrcs_study$cate) * 0.1)
top_indices <- order(cates_nrcs_study$cate, decreasing = TRUE)[1:n_top_10_percent]
constrained_optimum <- mean(c(cates_nrcs_study$cate[top_indices], -cates_nrcs_study$cate[-top_indices]))
rel_constrained_optimum <- 100 * constrained_optimum / baseline_mean

print(c(
  paste("blanket optimum: ", blanket_optimum, " (", rel_blanket_optimum,"%)", sep = ""),
  paste("unconstrained OLS optimum: ", unconstrained_optimum, " (", rel_unconstrained_optimum,"%)", sep = ""),
  paste("constrained OLS optimum: ", constrained_optimum, " (", rel_constrained_optimum,"%)", sep = "")
))
```


```{r plot cate estimates from nrcs}
# naive estimate from regressing differences on baseline
# nrcs_data <- nrcs_data %>% filter(TC_2016 < 8) # run this line to filter out the outlier
naive_estimates <- fitted(lm((TC_2019-TC_2016) ~ TC_2016, data = nrcs_data)) 
nrcs_naive_estimates <- data.frame(Y = naive_estimates, X = nrcs_data$TC_2016)

# estimate cate using ols
cate_estimates_grid <- estimate_cate(
  Y=nrcs_data$TC_2019, 
  Z=nrcs_data$treatment, 
  X=as.matrix(nrcs_data$TC_2016),
  learner = learner_ols,
  x_pop=as.matrix(baseline_soc_grid))
nrcs_cates_grid <- data.frame(X = baseline_soc_grid, Y = cate_estimates_grid$cate)

nrcs_cate_figure <- ggplot(nrcs_data, aes(x = TC_2016, y = TC_2019 - TC_2016)) +
  geom_point(aes(shape = treatment_long), size = 1.5) +
  scale_shape_manual(
    name = "Treatment",
    values = c(
      "Control" = 16,   # filled circle
      "Compost" = 17    # filled triangle
    )
  ) +
  new_scale_color() +
  geom_line(
    data = nrcs_cates_grid,
    aes(x = X, y = Y, color = "Causal (CATE)", linetype = "Causal (CATE)"),
    size = 1.2
  ) +
  geom_line(
    data = nrcs_naive_estimates,
    aes(x = X, y = Y, color = "Simple regression", linetype = "Simple regression"),
    size = 1.2
  ) +
  scale_color_manual(
    name = "Moderation estimate",
    values = c(
      "Causal (CATE)" = "steelblue",
      "Simple regression" = "darkorange3"
    )
  ) +
  scale_linetype_manual(
    name = "Moderation estimate",
    values = c(
      "Causal (CATE)"  = "solid",
      "Simple regression" = "dashed"
    )
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 18),
    legend.text = element_text(size = 14),
    legend.key.width = unit(1, "cm")
  ) +
  labs(
    x = "Baseline soil carbon (%)",
    y = "3-year change in soil carbon (%)"
  )

nrcs_cate_figure
```


## Intuition for how CATE is estimated

```{r cate intuition}
# Fit separate regressions for control and treatment groups
lm_control <- lm(TC_2019 ~ TC_2016, data = nrcs_data[nrcs_data$treatment == 0, ])
lm_treat   <- lm(TC_2019 ~ TC_2016, data = nrcs_data[nrcs_data$treatment == 1, ])

# Predict over the same baseline grid
intuition_grid <- data.frame(TC_2016 = baseline_soc_grid)
intuition_grid$control_pred <- predict(lm_control, newdata = intuition_grid)
intuition_grid$treat_pred   <- predict(lm_treat,   newdata = intuition_grid)
intuition_grid$cate_pred    <- intuition_grid$treat_pred - intuition_grid$control_pred

# Reshape to long for ggplot
intuition_long <- intuition_grid %>%
  pivot_longer(
    cols = c(control_pred, treat_pred, cate_pred),
    names_to  = "line",
    values_to = "y"
  ) %>%
  mutate(line = recode(line,
    "control_pred" = "Control regression",
    "treat_pred"   = "Treatment regression",
    "cate_pred"    = "CATE estimate"
  ))

cate_intuition_figure <- ggplot() +
  geom_point(
    data = nrcs_data,
    aes(x = TC_2016, y = TC_2019, shape = treatment_long, color = treatment_long),
    size = 1.5, alpha = 0.6
  ) +
  scale_shape_manual(
    name   = "Treatment",
    values = c("Control" = 16, "Compost" = 17)
  ) +
  scale_color_manual(
    name   = "Treatment",
    values = c("Control" = "darkorange3", "Compost" = "steelblue")
  ) +
  new_scale_color() +
  geom_line(
    data = intuition_long,
    aes(x = TC_2016, y = y, color = line, linetype = line),
    size = 1.2
  ) +
  scale_color_manual(
    name   = "Estimate",
    values = c(
      "Control regression"    = "darkorange3",
      "Treatment regression"  = "steelblue",
      "CATE estimate"     = "forestgreen"
    )
  ) +
  scale_linetype_manual(
    name   = "Estimate",
    values = c(
      "Control regression"    = "dashed",
      "Treatment regression"  = "dashed",
      "CATE estimate"     = "solid"
    )
  ) +
  theme_bw() +
  theme(
    text         = element_text(size = 18),
    legend.text  = element_text(size = 14),
    legend.key.width = unit(1, "cm")
  ) +
  labs(
    x = "Baseline %C ",
    y = "Follow-up %C or estimated treatment effect (%C)"
  )

cate_intuition_figure
```

### Plot-level Results

Plot-level results can be obtained by first aggregating to plots and then re-doing the same analysis.

```{r}
nrcs_plot_data <- nrcs_data %>%
  group_by(site, treatment, treatment_long) %>%
  summarize(TC_2016 = mean(TC_2016), TC_2019 = mean(TC_2019)) 

# naive estimate from regressing differences on baseline
naive_estimates <- fitted(lm((TC_2019-TC_2016) ~ TC_2016, data = nrcs_plot_data)) 
nrcs_naive_estimates <- data.frame(Y = naive_estimates, X = nrcs_plot_data$TC_2016)


cates_nrcs_study_plots <- estimate_cate(
  Y=nrcs_plot_data$TC_2019, 
  Z=nrcs_plot_data$treatment, 
  X=as.matrix(nrcs_plot_data$TC_2016),
  learner = learner_ols
)
```

Plot-level optimal policy returns

```{r}
# average treatment effect estimates (plot-level)
ATE_dim <- abs(
  mean(nrcs_plot_data$TC_2019[nrcs_plot_data$treatment == 1]) - 
  mean(nrcs_plot_data$TC_2019[nrcs_plot_data$treatment == 0])
)
blanket_optimum <- abs(ATE_dim)

# outcome on unconstrained optimal policy
unconstrained_optimum <- mean(abs(cates_nrcs_study_plots$cate))
rel_unconstrained_optimum <- 100 * unconstrained_optimum / baseline_mean
# treatment fraction for optimal policy
trt_frac <- mean(cates_nrcs_study_plots$cate > 0)

# outcome on treat 10% optimal policy 
n_top_10_percent <- ceiling(length(cates_nrcs_study_plots$cate) * 0.1)
top_indices <- order(cates_nrcs_study_plots$cate, decreasing = TRUE)[1:n_top_10_percent]
constrained_optimum <- mean(c(cates_nrcs_study_plots$cate[top_indices], -cates_nrcs_study_plots$cate[-top_indices]))
rel_constrained_optimum <- 100 * constrained_optimum / baseline_mean
print(c(
  paste("blanket optimum (plots): ", round(blanket_optimum, 3), " (", round(rel_blanket_optimum, 1),"%)", sep = ""),
  paste("unconstrained OLS optimum (plots): ", round(unconstrained_optimum, 3), " (", round(rel_unconstrained_optimum, 1),"%)", sep = ""),
  paste("constrained OLS optimum (plots): ", round(constrained_optimum, 3), " (", round(rel_constrained_optimum,1),"%)", sep = "")
))
```

Plot-level figure

```{r cate estimates at the plot-level}
# naive estimate from regressing differences on baseline
naive_estimates <- fitted(lm((TC_2019-TC_2016) ~ TC_2016, data = nrcs_plot_data)) 
nrcs_naive_estimates <- data.frame(Y = naive_estimates, X = nrcs_plot_data$TC_2016)

# estimate cate using ols
cate_estimates_grid <- estimate_cate(
  Y=nrcs_plot_data$TC_2019, 
  Z=nrcs_plot_data$treatment, 
  X=as.matrix(nrcs_plot_data$TC_2016),
  learner = learner_ols,
  x_pop=as.matrix(nrcs_plot_data$TC_2016))
nrcs_cates_grid <- data.frame(X = nrcs_plot_data$TC_2016, Y = cate_estimates_grid$cate)

nrcs_cate_figure <-  ggplot(nrcs_plot_data, aes(x = TC_2016, y = TC_2019 - TC_2016)) +
  geom_point(aes(shape = treatment_long), size = 1.5) +
  scale_shape_manual(
    name = "Treatment",
    values = c(
      "Control" = 16,   # filled circle
      "Compost" = 17    # filled triangle
    )
  ) +
  new_scale_color() +
  geom_line(
    data = nrcs_cates_grid,
    aes(x = X, y = Y, color = "Causal (CATE)", linetype = "Causal (CATE)"),
    size = 1.2
  ) +
  geom_line(
    data = nrcs_naive_estimates,
    aes(x = X, y = Y, color = "Simple regression", linetype = "Simple regression"),
    size = 1.2
  ) +
  scale_color_manual(
    name = "Moderation estimate",
    values = c(
      "Causal (CATE)" = "steelblue",
      "Simple regression" = "darkorange3"
    )
  ) +
  scale_linetype_manual(
    name = "Moderation estimate",
    values = c(
      "Causal (CATE)"  = "solid",
      "Simple regression" = "dashed"
    )
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 18),
    legend.text = element_text(size = 14),
    legend.key.width = unit(1, "cm")
  ) +
  labs(
    x = "Baseline soil carbon (%)",
    y = "3-year change in soil carbon (%)"
  )

nrcs_cate_figure
```

# Simulations

```{r simulation loop, eval = FALSE}
tic("simulations")
source("R/simulations.R")

############ parameters #############
Ns <- c(20, 40, 100, 200)
taus <- c(0, 0.2, 0.5, 1, 2)

scenarios <- list(
  list(label = "none",        scenario = "none"),
  list(label = "sat_small",   scenario = "saturation", beta = -0.2),
  list(label = "sat_large",   scenario = "saturation", beta = -1.0),
  list(label = "complex",   scenario = "complex", beta1 = -1.0, beta2 = -1.0)
)

num_sims <- 100
seed <- 123


########## simulation loop ###########
all_results <- list()
idx <- 1

for (N in Ns) {
  for (tau in taus) {
    for (sc in scenarios) {
      
      message(sprintf(
        "Running N=%d tau=%.2f scenario=%s",
        N, tau, sc$scenario
      ))
      
      all_results[[idx]] <- run_soc_simulation(
        N = N,
        tau = tau,
        scenario_params = sc,
        num_sims = num_sims,
        seed = seed,
        N_eval = 500
      )
      
      idx <- idx + 1
    }
  }
}

sim_df <- bind_rows(all_results)
save(sim_df, file = "../Data/simulation_results")
toc()
```

## Analyze simulation results

```{r}
load("../Data/simulation_results")

# summaries
sim_summary <- sim_df %>%
  group_by(N, tau, scenario) %>%
  summarise(
    oracle = mean(oracle),
    blanket = mean(blanket),
    ols = mean(ols),
    rf = mean(rf),
    ols_10 = mean(ols_10),
    rf_10 = mean(rf_10),
    .groups = "drop"
  ) %>%
  mutate(scenario_long = factor(case_match(
      scenario, 
      "none" ~ "No moderation", 
      "sat_small" ~ "Weak saturation", 
      "sat_large" ~ "Strong saturation",
      "complex" ~ "Complex moderation"
    ), levels = c("No moderation", "Weak saturation", "Strong saturation", "Complex moderation")))
```


```{r}
# percent regret relative to the oracle value
geom_mean <- function(x){exp(mean(log(x)))}
avg_pct_improvement <- sim_summary %>%
  mutate(
    improvement_oracle = 100 * oracle / blanket,
    improvement_ols = 100 * ols / blanket,
    improvement_rf = 100 *rf / blanket,
    improvement_ols10 = 100 * ols_10 / blanket,
    improvement_rf10 = 100 * rf_10 / blanket
  ) %>%
  group_by(tau, N, scenario_long) %>%
  filter(tau %in% c(0,1)) %>%
  filter(N %in% c(20, 200)) %>%
  summarize(
    oracle = round(geom_mean(improvement_oracle), 1), 
    ols = round(geom_mean(improvement_ols), 1), 
    rf = round(geom_mean(improvement_rf), 1), 
    ols10 = round(geom_mean(improvement_ols10), 1), 
    rf10 = round(geom_mean(improvement_rf10), 1))

# formatting for latex
table_latex <- avg_pct_improvement %>%
  mutate(
    tau = formatC(tau, format = "fg", digits = 1),
    
    oracle = paste0(formatC(oracle, format = "f", digits = 1), "\\%"),
    ols = paste0(formatC(ols, format = "f", digits = 1), "\\%"),
    rf = paste0(formatC(rf, format = "f", digits = 1), "\\%"),
    ols10 = paste0(formatC(ols10, format = "f", digits = 1), "\\%"),
    rf10 = paste0(formatC(rf10, format = "f", digits = 1), "\\%")
)

# print latex table
kable(
  table_latex,
  format = "latex",
  booktabs = TRUE,
  linesep = c("", "", "", "\\hline"),
  escape = FALSE,
  col.names = c(
    "ATE",
    "N",
    "Scenario",
    "Oracle",
    "OLS",
    "RF",
    "OLS Treat-10\\%)",
    "RF Treat-10\\%)"
  ),
  caption = "Average percent improvement in sequestration relative to the blanket policy."
) %>%
  kable_styling(latex_options = c("hold_position"))
```


```{r}
library(dplyr)
library(tidyr)
library(ggplot2)

plot_df <- sim_df %>%
  filter(!(scenario %in% c("complex_1", "complex_3"))) %>%
  mutate(
    regret_blanket = oracle - blanket,
    regret_ols = oracle - ols,
    regret_rf = oracle - rf,
    regret_ols_10 = oracle - ols_10,
    regret_rf_10 = oracle - rf_10
  ) %>%
  pivot_longer(
    cols = c(blanket, ols, rf, ols_10, rf_10),
    names_to = "policy",
    values_to = "policy_value"
  ) %>%
  mutate(
    regret = case_when(
      policy == "blanket" ~ regret_blanket,
      policy == "ols" ~ regret_ols,
      policy == "rf" ~ regret_rf,
      policy == "ols_10" ~ regret_ols_10,
      policy == "rf_10" ~ regret_rf_10
    ),
    policy = factor(
      policy,
      levels = c("blanket", "ols", "rf", "ols_10", "rf_10"),
      labels = c("Blanket", "OLS", "RF", "OLS 10%", "RF 10%")
    ),
    N = as.numeric(N),
    scenario_long = factor(case_match(
      scenario, 
      "none" ~ "No moderation", 
      "sat_small" ~ "Weak BL moderation", 
      "sat_large" ~ "Strong BL moderation",
      "complex" ~ "Complex moderation"
    ), levels = c("No moderation", "Weak BL moderation", "Strong BL moderation", "Complex moderation")),
    ATE = factor(paste("ATE: ", tau, "%", sep=""), levels = c("ATE: 0%", "ATE: 0.5%", "ATE: 1%", "ATE: 2%"))
  )
```


```{r}
regret_summary <- plot_df %>%
  filter(!(policy %in% c("OLS 10%", "RF 10%"))) %>%
  filter(!(tau %in% c(0.1,0.2))) %>%
  group_by(N, ATE, scenario_long, policy) %>%
  summarise(
    mean_regret = mean(regret),
    se_regret = sd(regret) / sqrt(n()),
    .groups = "drop"
  ) 

p_regret <- ggplot(regret_summary, aes(x = N, y = mean_regret, group = policy, linetype = policy, shape = policy, color = policy)) +
  geom_line() +
  geom_point(size = 2) +
  scale_color_manual(values = c("steelblue", "darkorange3", "darkgreen")) +
  xlim(0, 200) +
  facet_grid(scenario_long ~ ATE) +
  labs(
    x = "Study size (N)",
    y = "Mean regret relative to oracle (%SOC)",
    linetype = "Policy",
    shape = "Policy",
    color = "Policy"
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 16), 
    strip.text = element_text(size = 12),
    legend.text = element_text(size = 14),
    legend.key.width = unit(1, "cm")
  )

p_regret
```










